---
title: "Alcohol vs Seat choice"
author: "Alex Moreno"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.   
$H_A$: The average number drinks is different between at least two rows.  


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
From the plot, the ones in the back tend to get more alcohol than the front seats and middle. Middle has some max amounts at a higher level than the front. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The back seat shows a higher maximum than the others. Front seat being the one with the least spread of values.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The chart does show that the Back seating has the greatest maximum value. Also the highest mean value. While the front has the least values from the others. 

## Inferential Tests




## Conclusions


